Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-19 code/rmarkdown/article.Rmd
++ some article fixes + use PSOCK clusters (not SOCK) + use MLPE to correlate distances + use pcadapt + fix article + remove auto sorting from refs

```{r, include=FALSE}
# set wd
setwd('..')
setwd('..')

# load .rda file
try(session::restore.session('data/results/results.rda'))

@@

## Introduction
<!--  main text -->
The act of setting aside areas for preservation spearheads modern conservation efforts [@r440]. Protected area networks buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation underpins species persistence, and there has been increasing interest in understanding how to design protected area networks in a way that maximizes this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r48]. Adaptive genetic variation is associated with loci that affect fitness. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

Recently, conservation scientists have been investigating surrogates for genetic variation to generate better prioritizations without the overheads associated with genetic data. Since adaptive genetic variation is ultimately driven by extrinsic selection pressures, environmental variables have been used to guide reserve selection [eg. habitat conditions; @r247; @r2]. However, their effectiveness as surrogates in conservation planning remains unverified. On the other hand, neutral genetic variation arises from a reduction in gene flow between individuals. Surrogates for neutral variation are based on variables that predict the level of connectivity between planning units. For instance, the isolation by distance theory [IBD; @r259] predicts that populations further apart will have less connectivity, exchange less genetic material, and in turn have less genetic variation in common. Based on this theory, geographic distance-based surrogates have been found to improve prioritizations in an island network [@r200]. However this remains untested in spatially contiguous systems where connectivity is complicated by additional factors [eg. terrain; eg. @r474]--the very systems commonly featured in real-world conservation planning exercises [eg. @r197]. Before conservation planners can reliably use surrogates for genetic data in conservation planning, the effectiveness of these surrogates needs to be verified. Otherwise, conservation planners may waste precious resources on protecting places that provide little benefit to biodiversity.

@@

The IntroBioDiv project data set contains data for 27 alpine plant species that was collected using a 20' longitude by 21' latitude grid (approx. 22.3 km $\times$ 25 km; Figure S1). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using amplified fragment length polymorphisms [AFLP; @r453], and constructed matrices denoting the presence/absence of polymorphisms at loci for each species (mean `r mean(sapply(spp.StructureData.LST, n.loci))` \pm `r sd(sapply(spp.StructureData.LST, n.loci))` SD markers genotyped per species; see Table 1 in r@478 for the number markers for each species). Although AFLPs are not ideal as genomic representatives (cf. single nucleotide polymorphisms; SNPs), no multi-species genomic data set with similar properties currently exists. Thus the data set contains information describing the genomic properties of individuals for each species present in every second grid cell.

This data set has previously been used to address a range of different questions. Many studies have used this data set to explore patterns of adaptive [@r484; @r475; @r455; @r451; r@485] and neutral genetic variation [@r451; @r478; @r486]. However, to our knowledge, only a single study has used this data set to explore the effectiveness of a surrogate in the context of conservation planning. Taberlet et al. [-@r486] investigated whether prioritizations generated using the spatial distribution of a comprehensive set species (> 300) could adequately secure the intra-specific genetic variation for 27 species. They found that the prioritization based on species distributions was substantially different to that based on genomic data. Their results suggest that prioritizations based on species distribution data alone will be unable to secure intra-specific genetic variation.

@@

To describe the geographic location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted their two-dimensional coordinates. Thus we constructed two-dimensional geographic space-wherein each planning unit occupies a single point--as a potential surrogate for neutral genetic variation.

@@

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. To avoid falsely classifying loci as adaptive, we grouped individuals into genetic lineages for each species (Figures SXXX--SXXX). We used the number of genetic lineages in each species previously identified by Alvarez _et al._ [-@r478]. For each species, we used \texttt{Structure} (version 2.3.1; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species) and \texttt{ClumPP} (version 1.1.2; @r459) to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. To avoid false-positives, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the user manual) and assumed they were neutral. Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

@@

To address the second aim--to determine if the environmental and geographic variables are effect surrogates for adaptive and neutral genetic variation--we generated a collection of single-species prioritizations. For each species, we first generated two sets of prioritizations using increasing environmental and geographic-based targets (separately). Prioritizations were generated using the following surrogate-based targets: `r paste(rapr.params.LST[[MODE]]$surrogate.target,collapse=', ')`. We then create a set of null expectations with which to compare the surrogate-based prioritizations. These null expectations represented possible solutions obtained using conventional conservation planning methods that just use amount (eg. Marxan). For each species, for each target, we generated `r ` prioritizations by randomly selecting planning units occupied by the species. The number of randomly selected planning units was set to equal the number of planning units in the optimal prioritizations.

@@

We then counted the number of species that were sufficiently represented in terms of their adaptive and neutral genetic variation (genetic variation secured $\geq$ `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` %) for each prioritization. We used a global $G$ test to assess whether the proportion of species that met their genetic target in a given prioritization depended on the combination of targets used to generate the planning units (amount-based targets, amount and surrogate-based targets, amount and genetic-based targets), the planning scenario (single-species, multi-species, multi-species with cost), or the type of genetic variation measured (adaptive or neutral). We also conducted a post-hoc analysis involving pairwise $G$ tests [using the \texttt{RVAideMemoire R} package; r@483].

>>>>

```{r, include=FALSE}
# set wd
knitr::opts_knit$set(root.dir=normalizePath('../..'))
```

```{r,include=FALSE}
# load .rda file
try(session::restore.session('data/final/results.rda'))

@@

## Introduction
<!--  main text -->
Protected areas spearhead conservation efforts [@r440]. These places buffer species from anthropogenic impacts and provide places for species to persist. However, the resources available for conservation are limited. Thus protected areas need to be sited in places that achieve conservation goals for minimal cost. To ensure that protected areas are cost-effective, plans for protected areas (prioritizations) are often generated using decision support tools to identify near-optimal solutions. Additionally, because reserves cannot preserve the entire range for a given species, the plans for multiple reserves are often designed simultaneously to ensure that the network of protected areas can facilitate biological processes (eg. gene flow between populations, seasonal migration). For instance, \texttt{Marxan} [@r22] uses amount-based targets to identify protected area networks that preserve a suitable amount of habitat for each species (eg. 100 km $^2$ of land occupied by the species needs to be secured in a reserve) and weights to penalize fragmented solutions. However, conservation planning exercises typically assume that all individuals in the same species are equivalent.

Intra-specific genetic variation is an important component for species persistence. As a consequence, there has been increasing interest in understanding how to design prioritizations that preserve and cultivate this variation [@r67; @r3; @r61]. Although the strength of natural selection is a continuous force; broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r480]. Adaptive genetic variation is associated with loci that (significantly) affect fitness. Typically, such "adaptive" loci are detected due to anomalous patterns among individuals [eg. @r456; @r487; @r480; @r490; but see @r489 for alternative methods]. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not (significantly) affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. Thus protected areas networks should preserve both adaptive and neutral patterns of genetic variation for species of conservation interest [@r67; @r3]. Despite this, genetic data are not often used to inform prioritizations because they require considerable investment to obtain and analyze [@r61; but see @r5 and @r157 for developments on using genetic data in conservation planning]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

Recently, conservation scientists have been investigating surrogates to generate prioritizations that adequately preserve genetic variation--but without actually needing to utilize genetic data to do this. Since adaptive genetic variation is ultimately driven by extrinsic selection pressures, environmental variables have been used to guide reserve selection [eg. environmental conditions; @r247; @r2]. By preserving a more representative sampled of environmental conditions across the species' ranges, they aimed to generate prioritizations that preserved more adaptive variation. However, the effectiveness of this approach remains unverified. On the other hand, neutral genetic variation arises from a reduction in gene flow between individuals. Surrogates for neutral variation have been based on variables that predict the level of connectivity between planning units. For instance, the isolation by distance theory [IBD; @r259] predicts that populations further apart will have less connectivity, exchange less genetic material, and in turn have less genetic variation in common. Based on this theory, geographic distance-based surrogates have been found to improve prioritizations in an island network [@r200]. However this remains untested in spatially contiguous systems where connectivity is complicated by additional factors [eg. terrain; eg. @r474]--the very systems commonly featured in real-world conservation planning exercises [eg. @r197]. Before conservation planners can reliably use surrogates for genetic data in conservation planning, the effectiveness of these surrogates needs to be verified. Otherwise, conservation planners may waste precious resources on protecting places that provide little benefit to biodiversity.

@@

The IntroBioDiv project data set contains data for 27 alpine plant species that was collected using a 20' longitude by 21' latitude grid (approx. 22.3 km $\times$ 25 km; Figure S1). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using amplified fragment length polymorphisms [AFLP; @r453], and constructed matrices denoting the presence/absence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; see Table 1 in @r478 for the number markers for each species). Although AFLPs are not ideal as genomic representatives (cf. single nucleotide polymorphisms; SNPs), no multi-species genomic data set with similar properties currently exists. Thus the data set contains information describing the genomic properties of individuals for each species present in every second grid cell.

This data set has previously been used to address a range of different questions. Many studies have used this data set to explore patterns of adaptive [@r484; @r451; @r475; @r455; @r485] and neutral genetic variation [@r478; @r451; @r486]. However, to our knowledge, only a single study has used this data set to explore the effectiveness of a surrogate in the context of conservation planning. Taberlet _et al._ [-@r486] investigated whether prioritizations generated using the spatial distribution of a comprehensive set species (> 300) could adequately secure the intra-specific genetic variation for 27 species. They found that the prioritization based on species distributions was substantially different to that based on genomic data. Their results suggest that prioritizations based on species distribution data alone will be unable to secure intra-specific genetic variation.

@@

To describe the geographic location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted their two-dimensional coordinates. Thus we constructed two-dimensional geographic space--wherein each planning unit occupies a single point--as a potential surrogate for neutral genetic variation.

@@

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. To avoid falsely classifying loci as adaptive, we grouped individuals into genetic lineages for each species (Figures SXXX--SXXX). We used the number of genetic lineages in each species previously identified by Alvarez _et al._ [-@r478]. For each species, we used \texttt{Structure} [version 2.3.1; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species] and \texttt{ClumPP} [version 1.1.2; @r459] to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. To avoid false-positives, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the user manual) and assumed they were neutral. Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

@@

To address the second aim--to determine if the environmental and geographic variables are effect surrogates for adaptive and neutral genetic variation--we generated a collection of single-species prioritizations. For each species, we first generated two sets of prioritizations using increasing environmental and geographic-based targets (separately). Prioritizations were generated using the following surrogate-based targets: `r paste(rapr.params.LST[[MODE]]$surrogacy.analysis$surrogate.target,collapse=', ')`. We then create a set of null expectations with which to compare the surrogate-based prioritizations. These null expectations represented possible solutions obtained using conventional conservation planning methods that just use amount (eg. Marxan). For each species, for each target, we generated `r rapr.params.LST[[MODE]]$surrogacy.analysis$random.replicates` prioritizations by randomly selecting planning units occupied by the species. The number of randomly selected planning units was set to equal the number of planning units in the optimal prioritizations.

@@

We then counted the number of species that were sufficiently represented in terms of their adaptive and neutral genetic variation (genetic variation secured $\geq$ `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` %) for each prioritization. We used a global $G$ test to assess whether the proportion of species that met their genetic target in a given prioritization depended on the combination of targets used to generate the planning units (amount-based targets, amount and surrogate-based targets, amount and genetic-based targets), the planning scenario (single-species, multi-species, multi-species with cost), or the type of genetic variation measured (adaptive or neutral). We also conducted a post-hoc analysis involving pairwise $G$ tests [using the \texttt{RVAideMemoire R} package; @r483].

### 2016-04-19 code/rmarkdown/figures.Rmd
++ some article fixes + use PSOCK clusters (not SOCK) + use MLPE to correlate distances + use pcadapt + fix article + remove auto sorting from refs

```{r, include=FALSE}
# set wd
setwd('..')
setwd('..')

# load .rda file
try(session::restore.session('data/results/results.rda'))

@@

```{r, echo=FALSE, message=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. White boxplots show the proportion of genetic variation secured by prioritizations generated using surrogate-based targets. Grey boxplots show the proportion of genetic variation secured by randomly generated prioritizations with the same number of planning units as the surrogate-based prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets.'}
# prepare data
correlation.PDF <- correlation.sub.DF %>%
	group_by(Type, Surrogate.target, Method, Species) %>% 
	summarize(genetic.held=mean(genetic.held, na.rm=TRUE)) %>%
	data.frame()

# make figure
p1 <- ggplot(aes(x=Surrogate.target,y=genetic.held, fill=Method),
		data=filter(correlation.PDF, Type=='Environmental')) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Environmental surrogate target (%)') + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.115, label='(a)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position=c(0.9,0.4)) +
	scale_fill_manual(name='Prioritization', values=c('Optimal'='white', 'Random'='grey50'))

p2 <- ggplot(aes(x=Surrogate.target,y=genetic.held, fill=Method),
			data=filter(correlation.PDF, Type=='Geographic')) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Geographic surrogate target (%)') + 
	ylab('Neutral genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.115, label='(b)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position='none') +
	scale_fill_manual(name='Prioritization', values=c('Optimal'='white', 'Random'='grey50'))

>>>>

```{r, include=FALSE}
# set wd
knitr::opts_knit$set(root.dir=normalizePath('../..'))
```

```{r, include=FALSE}
# load .rda file
try(session::restore.session('data/final/results.rda'))

@@

```{r, echo=FALSE, message=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. White boxplots show the proportion of genetic variation secured by prioritizations generated using surrogate-based targets. Grey boxplots show the proportion of genetic variation secured by randomly generated prioritizations with the same number of planning units as the surrogate-based prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets.'}
# prepare data
surrogacy.PDF <- surrogacy.DF %>%
	group_by(Type, Surrogate.target, Method, Species) %>% 
	summarize(genetic.held=mean(genetic.held, na.rm=TRUE)) %>%
	data.frame()

# make figure
p1 <- ggplot(aes(x=Surrogate.target,y=genetic.held, fill=Method),
		data=filter(surrogacy.PDF, Type=='Environmental')) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Environmental surrogate target (%)') + 
	ylab('Adaptive genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.115, label='(a)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position=c(0.9,0.4)) +
	scale_fill_manual(name='Prioritization', values=c('Optimal'='white', 'Random'='grey50'))

p2 <- ggplot(aes(x=Surrogate.target,y=genetic.held, fill=Method),
			data=filter(surrogacy.PDF, Type=='Geographic')) +
	geom_boxplot(position=position_dodge(0.9)) +
	xlab('Geographic surrogate target (%)') + 
	ylab('Neutral genetic\nvariation secured (%)') +
	geom_text(aes(x=0.55, y=1.115, label='(b)'), color='black', size=5) +
	theme_classic() +
	theme(legend.position='none') +
	scale_fill_manual(name='Prioritization', values=c('Optimal'='white', 'Random'='grey50'))

### 2016-04-19 code/rmarkdown/supporting_information.Rmd
+ updates to directory structure + use structure for analysis
++ some article fixes + use PSOCK clusters (not SOCK) + use MLPE to correlate distances + use pcadapt + fix article + remove auto sorting from refs

```{r, include=FALSE}
# set wd
setwd('..')

# load .rda file
try(session::restore.session('results/results.rda'))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Each line denotes a different model parametrization. Asterisks indicate the model and number of populations with the most support.'}
# format data
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		curr.MTX <- spp.Mclust.LST[[i]]$mclust$BIC
		attr(curr.MTX, 'dim') <- c(nrow(curr.MTX), ncol(curr.MTX))
		attr(curr.MTX, 'dimnames') <- list(
			seq_len(nrow(curr.MTX)),
			attr(curr.MTX, 'modelNames')
		)
		class(curr.MTX) <- 'matrix'
		curr.DF <- curr.MTX %>% as.data.frame %>% 
			mutate(G=attr(curr.MTX, 'G')) %>% 
			gather(Model,BIC,-G)
		curr.DF$BIC=curr.DF$BIC*-1
		return(
			mutate(
				curr.DF,
				Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE),
				best_G=curr.DF[which.min(curr.DF$BIC),'G'][[1]],
				best_stat=min(curr.DF$BIC,na.rm=TRUE),
				asterisk_col=c('black', rep(NA_character_, length(Species)-1))
			)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_line(aes(y=BIC, x=G, color=Model, linetype=Model)) +
		geom_point(aes(y=best_stat, x=best_G), size=4, shape=8) +
		theme_classic() +
		scale_y_reverse()+
		theme(
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', face='italic', size=1)
		) +
		xlab('Number of populations') +
		ylab('BIC') +
		scale_linetype_manual(values=rep(c('solid','dashed'),each=7)) +
		scale_color_manual(values=rep(gg_color_hue(7),2)) +
		facet_wrap(~ Species, ncol=4, scales='free_y')
})
```

@@

		curr.probs <- spp.Mclust.LST[[i]]$mclust$z %>%

@@

```{r, echo=FALSE}
knitr::kable(
	format.dataframe(
		filter(
			ldply(
				seq_along(unique(spp.samples.DF$species)), 
				function(i) {
					rbind(
						data.frame(
							Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
							Loci='all',
							k=spp.Mclust.LST[[i]]$nmds$ndim,
							Stress=spp.Mclust.LST[[i]]$nmds$stress,
							Converged=spp.Mclust.LST[[i]]$nmds$converged
						),
						ldply(
							seq_along(spp.nmds.LST[[i]]),
							function(j) {
								data.frame(
									Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
									Loci=names(spp.nmds.LST[[i]])[j],
									k=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_integer_, spp.nmds.LST[[i]][[j]]$ndim),
									Stress=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA_real_, spp.nmds.LST[[i]][[j]]$stress),
									Converged=ifelse(is.null(spp.nmds.LST[[i]][[j]]), NA, spp.nmds.LST[[i]][[j]]$converged)
								)
						})
					)
				}
			),
			!is.na(Stress)
		),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species. The analyses on all loci were used to transform the binary presence/absence polymorphism data to continuous variables to train Gaussian mixture models and ultimately identify adaptive loci. The analyses on adaptive and neutral loci were used to transform the polymorphism data to identify main gradients of this variation.',
	col.names=c('Species', 'Loci Type', 'k', 'NMDS Stress', 'Converged'),
	align=c('c', 'c', 'c', 'c', 'c')
)
```

```{r, echo=FALSE}
loci_classification.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)), 
	function(i) {
		if (!is.null(spp.BayeScan.sample.loci.subset.LST[[i]])) {
			data.frame(
				Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
				Primer=spp.BayeScan.LST[[i]]$bayescan@data@primers,

				Bayescan_Probability=spp.BayeScan.LST[[i]]$bayescan@results@summary[[2]],
				Bayescan_qval=spp.BayeScan.LST[[i]]$bayescan@results@summary[[4]],
				Bayescan_alpha=spp.BayeScan.LST[[i]]$bayescan@results@summary[[5]],
				Bayescan_fst=spp.BayeScan.LST[[i]]$bayescan@results@summary[[6]],
				Bayescan_Type=spp.BayeScan.LST[[i]]$bayescan@results@summary[[7]],

				PCadapt_K=spp.pcadapt.LST[[i]]$K,
				PCadapt_chi2_statistic=spp.pcadapt.LST[[i]]$chi2.stat,
				PCadapt_pvalue=spp.pcadapt.LST[[i]]$pvalues,
				PCadapt_Type=replace(rep('neutral, length(spp.pcadapt.LST[[i]]$pvalues)), spp.pcadapt.LST[[i]]$adaptive.loci, 'adaptive')

				Overall_Type=replace(rep('neutral, length(spp.pcadapt.LST[[i]]$pvalues)), spp.OutlierDetectionResults.LST[[i]], 'adaptive')
			)
		}
	}
)

# save to file
write.table(loci_classification.DF, 'article/Table_S2', sep=',', row.names=FALSE)
```

>>>>

```{r, include=FALSE}
# set wd
knitr::opts_knit$set(root.dir=normalizePath('../..'))
```

```{r, include=FALSE}
# load .rda file
try(session::restore.session('data/final/results.rda'))

@@

@@

		curr.probs <- spp.StructureAnalysis.LST[[i]]@results@summary %>%

@@

```{r, echo=FALSE}
loci_classification.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)), 
	function(i) {
		if (!is.null(spp.BayeScan.LST[[i]])) {
			data.frame(
				Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
				Primer=spp.BayeScan.LST[[i]]$bayescan@data@primers,

				Bayescan_fst=spp.BayeScan.LST[[i]]$bayescan@results@summary[[6]],
				Bayescan_Probability=spp.BayeScan.LST[[i]]$bayescan@results@summary[[2]],
				Bayescan_alpha=spp.BayeScan.LST[[i]]$bayescan@results@summary[[5]],
				Bayescan_qvalue=spp.BayeScan.LST[[i]]$bayescan@results@summary[[4]],
				Bayescan_Type=spp.BayeScan.LST[[i]]$bayescan@results@summary[[7]],

				PCadapt_K=spp.pcadapt.LST[[i]]$K,
				PCadapt_chi2_statistic=spp.pcadapt.LST[[i]]$stats$chi2.stat,
				PCadapt_pvalue=spp.pcadapt.LST[[i]]$pvalues,
				PCadapt_qvalue=spp.pcadapt.LST[[i]]$qvalues$qvalues,
				PCadapt_Type=replace(rep('neutral', length(spp.pcadapt.LST[[i]]$pvalues)), spp.pcadapt.LST[[i]]$adaptive.loci, 'adaptive'),

				Overall_Type=replace(rep('neutral', length(spp.pcadapt.LST[[i]]$pvalues)), spp.OutlierDetectionResults.LST[[i]], 'adaptive')
			)
		}
	}
)

write.table(loci_classification.DF, 'article/Table_S2.csv', sep=',', row.names=FALSE)
```
